Notebook of learning from ensemble labels

### 2021-07-27 docs/notebook_learn_dl_ensemble.Rmd
Fix parse dataset bug and modify a few parameters

```
python hrlcm/fit_compose_lr.py --exp_name unet_single_gl --lowest_score 9 --num_workers 32 --gpu_devices '0,1,2,3'
```

```
python hrlcm/fit_coteaching.py --exp_name unet_cot_8 --highest_score 8 --lowest_score 8 --num_workers 32 --gpu_devices '0,1,2,3'
```

>>>>

```
python hrlcm/fit_step_lr.py --exp_name unet_slr --num_workers 32 --gpu_devices '0,1,2,3'
```

```
python hrlcm/fit_compose_lr.py --exp_name unet_clr --num_workers 32 --gpu_devices '0,1,2,3'
```
